\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-09-25 NAR_DRAFT.tex
kl divergence is not symmetric

\begin{figure}
  \begin{center}
  \includegraphics{figures/kl_only.pdf}
  \end{center}
  \caption{Convergence of the site-specific prior to the data generating distribution. Plotted is the Kullback-Leibler divergence between the estimated and simulated profiles versus number of incorporated mutations for whole exomes. Convergence for whole genomes is similar.
  \rngcomment{Omit panel B and remove A label. These are similar enough we don't need to show both.}
  }
\label{NAR-kl_fig}
\end{figure}

@@

  \begin{figure*}
    \begin{center}
    \includegraphics[width=\textwidth]{figures/fig_wes.pdf}
    \end{center}
    \caption{Variant-calling performance on both simulated and real data.
    \textbf{(A)} Precision-recall curves and \textbf{(B)} receiver operating characteristic curves for different mutation signatures.
    \textbf{(C)} and \textbf{(D)} Shaded regions show distributions of posterior probabilities for tree positive variants, and the smooth line shows the loess-smoothed relationship, from which the Integrated Calibration Index is calculated. For a perfectly calibrated caller, that curve would match the dashed y=x line. 
    \textbf{(E)} and \textbf{(F)} Precision-recall curves for real data in which substantial validation was performed \cite{Griffith2015,Shi2018}.
    \rngcomment{Wasting a ton of vertical space now. Remove extraneous whitespace throughout. For panels A,B,E\&F, make \batcave curve thicker, so it's visible from behind the MuTect curve.}
}
  \label{NAR-wes_fig}
  \end{figure*}

>>>>

\begin{figure}
  \begin{center}
  \includegraphics{figures/kl_only.pdf}
  \end{center}
  \caption{Convergence of the site-specific prior to the data generating distribution. Plotted is the Kullback-Leibler divergence between the simulated and estimated profiles versus number of incorporated mutations for whole exomes. Convergence for whole genomes is similar.
  }
\label{NAR-kl_fig}
\end{figure}

@@

  \begin{figure*}
    \begin{center}
    \includegraphics[width=\textwidth]{figures/fig_wes.pdf}
    \end{center}
    \caption{Variant-calling performance on both simulated and real data.
    \textbf{(A)} Precision-recall curves and \textbf{(B)} receiver operating characteristic curves for different mutation signatures.
    \textbf{(C)} and \textbf{(D)} Shaded regions show distributions of posterior probabilities for tree positive variants, and the smooth line shows the loess-smoothed relationship, from which the Integrated Calibration Index is calculated. For a perfectly calibrated caller, that curve would match the dashed y=x line. 
    \textbf{(E)} and \textbf{(F)} Precision-recall curves for real data in which substantial validation was performed \cite{Griffith2015,Shi2018}.
}
  \label{NAR-wes_fig}
  \end{figure*}
